%-------------------------
% Resume in Latex
% Author : LYSANDRO CARIOCA BRAGA
% License : MIT
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% Ensure that generate pdf is machine readable/ATS parsable

%\input glyphtounicode
%\pdfgentounicode=1
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://linkedin.com/in/lysandroc}{\Large LYSANDRO CARIOCA BRAGA}} & Fortaleza, Ceara, Brazil\\ 
  \href{https://linkedin.com/in/lysandroc}{\faLinkedin \ @lysandroc}
  \href{https://github.com/lysandroc}{\faGithub \ @lysandroc} & Mobile: +55 85 997-569-542\\
  \textbf{}{} & Email: \href{mailto:lysandroc@gmail.com}{lysandroc@gmail.com} \\
\end{tabular*}
\hfill \break
Software engineer with eight years of experience developing and scaling applications. Outstanding problem solver with an aptitude for troubleshooting and the ability to quickly master new skill technology.
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    {\item
      \textbf{Languages}{: Javascript, Typescript, Golang, Java, C\# and SQL}
     }
     \hfill
     {\item
      \textbf{Technologies}{: React, Jest, Cypress, NodeJS, AWS, Kubernetes, RabbitMQ, CouchDB and ScyllaDB}
     }
  \resumeSubHeadingListEnd
  
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SysMap Solutions Software} {}
      {Senior Software Engineer}{Feb. 2021 - Present}
      \resumeItemListStart
        \resumeItem{Global Relationship Platform}
          {Creating a new product for \href{https://naturaeco.com/en/}{Natura\&Co} to keep track of the beauty consultant relationship time in several countries. Implementing an event-driven design architecture to calculate asynchronous relationship time using AWS Lambda, AWS SQS, NodeJS, and ScyllaDB. Adding new features in a NodeJS and ReactJS application. Monitoring applications through Grafana, Kibana, and Kubernetes.}
      \resumeItemListEnd
  
    \resumeSubheading
      {Instituto Atlântico} {}
      {Senior Software Engineer}{Apr. 2020 - Feb. 2021}
      \resumeItemListStart
        \resumeItem{\href{https://www.printos.com}{3D Printer Dashboard}}
          {Developed a system a as service for HP that shows all information about 3D printer usage. Implemented a thin REST layer written in Golang that reads information from the AWS Redshift; Created dashboards from Figma using React, React Hooks, Typescript; Contributed to the internal DevOps organization creating yaml template steps used across multiple teams. }
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://osf.digital/}{OSF Digital}} {}
      {Senior Software Engineer}{May 2019 - Apr. 2020}
      \resumeItemListStart
        \resumeItem{\href{https://autocompra.caixavidaeprevidencia.com.br/previdencia/objetivo}{Private Pension}}
          {A solution that offers a private pension fund to customers. Developed a web application from scratch using ReactJS, React Hooks, Context API, RTL, and Styled Components from Sketch UI; Code was covered by 85\% of unit testing; Led a team of three developers to build an end to end testing project using the cypress framework.   }
          \resumeItem{Open Banking API}
          {Open Banking is a project that reduces the bank transaction price for customers. Implemented an application using ReactJS that reads API Specification and shows samples on how to use this in different languages; Implemented new rules using Java and RabbitMQ inside the event-driven flow that processes data asynchronously.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.paguemenos.com.br/}{Drugstore Pague Menos}}{Fortaleza, CE}
      { Team Leader, Senior Software Engineer}{Aug. 2013 - Apr. 2019}
      \resumeItemListStart
        % \resumeItem{Leadership}
        %   {Led a team of ten during three years to develop supply chain solutions for five warehouses and more than a thousand stores.}
        \resumeItem{Last Chance}
          {A system that applies discounts for products near expiration date used by more than a thousand stores. I developed this application using ReactJS and .NET Core within five months and it increased the sales by around a million dollars monthly. }
        \resumeItem{Warehouse Order Picking System}
          {A distributed system and data over CouchDB used to check and validate the picking process using the pick box method. Implemented a sample method algorithm to pick random boxes and reduce issues using Javascript; Optimized routines to clean up the local database on hundreds of workstations using NodeJS; Optimized the picking process from 2 hours to 5 minutes grouping them by transport routes. }
      \resumeItemListEnd
    % \resumeSubSubheading
    %  {Software Developer Intern}{Feb. 2013 - Aug. 2013}
    %  \resumeItemListStart
    %     \resumeItem{Maintainer}
    %       {Included SQL queries in the purchases and sales reports; Implemented a new application using ASP.NET to record client information by pharmacists.}
    %  \resumeItemListEnd
    \resumeSubHeadingListEnd

% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Postgraduate Diploma in Software Engineering}{Fortaleza, CE}
      {Universidade Estadual do Ceara}{May. 2017 -- Feb. 2019}
    \resumeSubheading
      {Associate of Science in Computer Science}{Fortaleza, CE}
      {Faculdade Tecnologica Lourenço Filho}{Feb. 2012 -- Dec. 2014}
    % \resumeSubheading
    %   {EEEP Santa Rita}{Maranguape, CE}
    %   {Computer Technician}{Feb. 2009 -- Dec. 2011}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{Github Visualization}
%      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
% \resumeSubHeadingListEnd
%
%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}